Verifying Demonstrations

### 2018-02-28 paper/AdaptingPROPS.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

One issue is the \ac{CA}.
One direction we can take to solve this is by threshold signatures, e.g.\ 
\cite{FSThresholdSignatures}.
This way the participants can jointly issue new certificates, by signing them 
using the threshold signature scheme.
This should solve part of the problems related to Sybil attacks too.
But, if \(k > t\) participants collude, they can create multiple identities for 
themselves.
The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
too, to change with the number of participants.
I'm not sure, but in what I've read about threshold schemes, they generally 
keep \(n\) and \(t\) fixed.

Another direction on solving the \ac{CA} problem, is if we can use already 
existing \acp{PKI} instead.
E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
running everything through a hash function and the sign that value.
Due to the use of the hash function we cannot prove in zero knowledge that we 
have a signed certificate.
But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
they do not reveal the identity, but that we can if needed --- similar to 
a commitment which we reveal only in emergencies.

It would be interesting to solve the W--P collusion attack, where the witness 
reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
individuals fake this information at home.
One possibility in our scenario is that e.g.\ an external journalist on 
location can create \iac{LPS}, because a journalist is generally trusted.
This would be useful as occasionally journalists are also captured, and anyone 
that escaped should be able to show a convincing proof.
However, one problem with this is that the journalist will not necessarily have 
a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
\ac{PKI}.

In relation to the previous, it would be interesting to be able to tie the 
\acp{LP} (or \acp{LPS}) to a reputation system.
Then, even if no external journalist is on location, the participants can rely 
on their online reputation.
One option would be to have a reputation system in a global location-proof 
system, another would be to tie it to a reputation system already used in e.g.\ 
\iac{OSN}.
One possible solution would be to include a commitment in the \ac{LPS} and when 
necessary use it to tie it to the online identity.

@@

To make it even more efficient, it would be desirable to make the proofs 
\enquote{transitive}.
I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
Speaking in graphs, we want to be able to join sub-graphs instead of having to 
join node-by-node.

>>>>

One issue is the \ac{CA}.
One direction we can take to solve this is by threshold signatures, \eg 
\cite{FSThresholdSignatures}.
This way the participants can jointly issue new certificates, by signing them 
using the threshold signature scheme.
This should solve part of the problems related to Sybil attacks too.
But, if \(k > t\) participants collude, they can create multiple identities for 
themselves.
The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
too, to change with the number of participants.
I'm not sure, but in what I've read about threshold schemes, they generally 
keep \(n\) and \(t\) fixed.

Another direction on solving the \ac{CA} problem, is if we can use already 
existing \acp{PKI} instead.
\Eg Sweden has a deployed national \ac{eID} system; usually these are RSA or 
DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
running everything through a hash function and the sign that value.
Due to the use of the hash function we cannot prove in zero knowledge that we 
have a signed certificate.
But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
they do not reveal the identity, but that we can if needed --- similar to 
a commitment which we reveal only in emergencies.

It would be interesting to solve the W--P collusion attack, where the witness 
reports false \acp{LPS}, \eg we would need to prevent that a group of 
individuals fake this information at home.
One possibility in our scenario is that \eg an external journalist on 
location can create \iac{LPS}, because a journalist is generally trusted.
This would be useful as occasionally journalists are also captured, and anyone 
that escaped should be able to show a convincing proof.
However, one problem with this is that the journalist will not necessarily have 
a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
\ac{PKI}.

In relation to the previous, it would be interesting to be able to tie the 
\acp{LP} (or \acp{LPS}) to a reputation system.
Then, even if no external journalist is on location, the participants can rely 
on their online reputation.
One option would be to have a reputation system in a global location-proof 
system, another would be to tie it to a reputation system already used in \eg 
\iac{OSN}.
One possible solution would be to include a commitment in the \ac{LPS} and when 
necessary use it to tie it to the online identity.

@@

To make it even more efficient, it would be desirable to make the proofs 
\enquote{transitive}.
\Ie if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
Speaking in graphs, we want to be able to join sub-graphs instead of having to 
join node-by-node.

### 2018-02-28 paper/RelatedWork.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
based on a selected space.
Then the user selects one of three pre-set density estimates: light, medium or 
dense.
This is similar to the method usually used by police, e.g.\ for the protests in
Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, 
then it inherits the verifiability properties of the previous method.

There is a body of work in the computer vision community, e.g.\ the work of 
\citet{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
algorithm on different scenes, which might make this method easier to use for 
protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
this might still be difficult. Automatic face recognition can help
verifiability but at the price of privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method 
can provide a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above, i.e.\ forensic methods.

@@

A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
towers of the mobile network) to count unique phones at the location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the 
counter-protesters.
Second, since the phone is a unique identifier, participants might be 
uncomfortable to be registered in association with the event and might thus 
turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be 
trusted to record all data and do it in the relation to the event.

@@

In general for all of the above methods, the more a crowd spreads out, the more
difficult it will be to determine its size:
the problem is determining whether people near the event's perimeter are 
participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty capturing the actual attendance of an event,
i.e.\ the cumulative participation, not just the count at a snapshot around the 
peak.

One of the most closely related work is \citet{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

>>>>

There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
based on a selected space.
Then the user selects one of three pre-set density estimates: light, medium or 
dense.
This is similar to the method usually used by police, \eg for the protests in
Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, 
then it inherits the verifiability properties of the previous method.

There is a body of work in the computer vision community, \eg the work of 
\citet{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
algorithm on different scenes, which might make this method easier to use for 
protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
this might still be difficult. Automatic face recognition can help
verifiability but at the price of privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method 
can provide a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above, \ie forensic methods.

@@

A better proposal would be to use \emph{IMSI catchers} (or the real cell 
towers of the mobile network) to count unique phones at the location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the 
counter-protesters.
Second, since the phone is a unique identifier, participants might be 
uncomfortable to be registered in association with the event and might thus 
turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be 
trusted to record all data and do it in the relation to the event.

@@

In general for all of the above methods, the more a crowd spreads out, the more
difficult it will be to determine its size:
the problem is determining whether people near the event's perimeter are 
participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty capturing the actual attendance of an event,
\ie the cumulative participation, not just the count at a snapshot around the 
peak.

One of the most closely related work is \citet{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, \ie the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if \eg Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

### 2018-02-28 paper/SystemModel.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{multline}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid \right. \\
    \left. pid = i, cid = j,
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (i.e.\ \(t_j\) and \(l_j\)).
\end{definition}

>>>>

\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{multline}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid \right. \\
    \left. pid = i, cid = j,
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (\ie \(t_j\) and \(l_j\)).
\end{definition}

### 2018-02-28 paper/TimeStamp.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

We will use the storage to provide the temporal eligibility property.
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.
One primitive that fulfils these requirements is a blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
properties.
However, we will use the blockchain in our discussion for simplicity.

There are five properties that we need from the storage system, all of which 
makes a blockchain-like structure suitable.
First, we need immutability.
I.e.\ once we commit something to the blockchain it will remain there.
We will use this to ensure verifiability, the data must remain to be verifiable.

Second, we need a general form of time-stamping.
I.e.\ we must be able to relate commitments to time, e.g.\ in 
Bitcoin~\cite{Bitcoin} a new block appears approximately every 10 minutes.
This coarse-grained form of time-stamping is enough for our purposes.
We will use this property to ensure that proofs are created before a certain 
point in time.

@@

Fourth, once we have committed some data, we do not need to keep the data 
itself, but we can store some confirmation value instead.
E.g.\ using blockchains, we can store the hash of the block where our data was 
committed, while this block remains we are sure that our data remains committed 
--- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

>>>>

We will use the storage to provide the temporal eligibility property.
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.
One primitive that fulfils these requirements is a blockchain.
There are also other structures, \eg a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
properties.
However, we will use the blockchain in our discussion for simplicity.

There are five properties that we need from the storage system, all of which 
makes a blockchain-like structure suitable.
First, we need immutability.
\Ie once we commit something to the blockchain it will remain there.
We will use this to ensure verifiability, the data must remain to be verifiable.

Second, we need a general form of time-stamping.
\Ie we must be able to relate commitments to time, \eg in 
Bitcoin~\cite{Bitcoin} a new block appears approximately every 10 minutes.
This coarse-grained form of time-stamping is enough for our purposes.
We will use this property to ensure that proofs are created before a certain 
point in time.

@@

Fourth, once we have committed some data, we do not need to keep the data 
itself, but we can store some confirmation value instead.
\Eg using blockchains, we can store the hash of the block where our data was 
committed, while this block remains we are sure that our data remains committed 
--- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

### 2018-02-28 paper/properties.tex
Changes order of sections, changes PRF to \PRF
coincoin
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
Alice the activist (and all the protesters) try to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants to arrest them or 
\enquote{convince} them to change their minds.
Finally, we have Rusuk who is represents another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice as he see fits.
Rusuk will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

@@

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

>>>>

We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
Alice the activist (and all the protesters) try to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants to arrest them or 
\emph{convince} them to change their minds.
Finally, we have Rusuk who is represents another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice as he see fits.
Rusuk will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

@@

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
\eg Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

### 2018-02-28 paper/protocol.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

\section{PRIVO: A protocol for protest outcome verification}
\label{protocol}

We will start by giving an overview of the protocol.
We have a number of participants.
We have a cothority who provide the storage in a decentralized manner.
The cothority should consist of independent actors, preferably with conflicting 
interests so that they will not collude.
We have Alice the organizer and Bob the participant who are both protesters.
We have the trustworthy journalist Jane who is present but not participating in 
the protest.
The protesters will witness each others participation proofs, e.g.\ Alice will 
witness Bob's proof and Bob will witness Alice's proof.
The result of witnessing a proof is a proof share (essentially a witness 
signature).
Jane will also participate in witnessing the protesters' proofs.
The witnessing is done through local interaction.
As soon as Alice and Bob have departed from the protest they upload their proofs 
(i.e.\ all proof shares) to the cothority for indefinite storage.
Since each proof consists of one proof share for each witness, each witness 
could potentially upload the proof share themselves to the cothority.
This would have the same effect but with added redundancy, in case Alice or Bob 
cannot upload them themselves.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one individual 
can provide two participation proofs and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event.
E.g.\ there might be a counter protest at the same time and place, these would 
have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
The idea is to construct a unique identifier for a protest.

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets \PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

@@

According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
(shares) spatially to the location, which would allow us to verify that they 
were actually in that location.
The role of the witnesses, e.g.\ Jane, is to provide this property.
Jane can do this by using a distance-bounding protocol to ensure that the secret 
associated with Alice or Bob must be within limited physical distance.

@@

We note that there are at least two entities who know each proof share, the 
protester and the witness.
Alice and Bob simply commit their proofs (i.e.\ all proof shares of their 
proofs) to the blockchain as soon as possible after they have participated in 
the protest.
The witnesses do the same, they commit all the proof shares that they helped 
create.
(Shown in \cref{fig:ProtocolOverview}.)

@@

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, i.e.\ of all its shares.
Second, we must count these valid proofs.
Third, each protester must check that their proof is indeed registered so that 
it can be counted.

@@

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

@@

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  \PRF_{k_W}(pid)\) and \(wsig = \PRF_{k_W}(wid, t_s, l)\) as well as that the 
witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
eligibility, of the proof shares and thus also count them.

>>>>

\section{\PRIVO:\@ A protocol for protest outcome verification}%
\label{protocol}

We will start by giving an overview of the protocol.
We have a number of participants.
We have a cothority who provide the storage in a decentralized manner.
The cothority should consist of independent actors, preferably with conflicting 
interests so that they will not collude.
We have Alice the organizer and Bob the participant who are both protesters.
We have the trustworthy journalist Jane who is present but not participating in 
the protest.
The protesters will witness each others participation proofs, \eg Alice will 
witness Bob's proof and Bob will witness Alice's proof.
The result of witnessing a proof is a proof share (essentially a witness 
signature).
Jane will also participate in witnessing the protesters' proofs.
The witnessing is done through local interaction.
As soon as Alice and Bob have departed from the protest they upload their proofs 
(\ie all proof shares) to the cothority for indefinite storage.
Since each proof consists of one proof share for each witness, each witness 
could potentially upload the proof share themselves to the cothority.
This would have the same effect but with added redundancy, in case Alice or Bob 
cannot upload them themselves.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event.
\Eg there might be a counter protest at the same time and place, these would 
have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
The idea is to construct a unique identifier for a protest.

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, \eg by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets \PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

@@

According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
(shares) spatially to the location, which would allow us to verify that they 
were actually in that location.
The role of the witnesses, \eg Jane, is to provide this property.
Jane can do this by using a distance-bounding protocol to ensure that the secret 
associated with Alice or Bob must be within limited physical distance.

@@

We note that there are at least two entities who know each proof share, the 
protester and the witness.
Alice and Bob simply commit their proofs (\ie all proof shares of their 
proofs) to the blockchain as soon as possible after they have participated in 
the protest.
The witnesses do the same, they commit all the proof shares that they helped 
create.
(Shown in \cref{fig:ProtocolOverview}.)

@@

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, \ie of all its shares.
Second, we must count these valid proofs.
Third, each protester must check that their proof is indeed registered so that 
it can be counted.

@@

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (\ie of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

@@

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  \PRF_{k_W}(pid)\) and \(wsig = \PRF_{k_W}(wid, t_s, l)\) as well as that the 
witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
eligibility, of the proof shares and thus also count them.
